toyData

### 2017-01-29 latex/article_vol2.tex
Fix package reference
Updated article

\section{Introduction}
Though data cleaning might be regarded as a somewhat tedious activity,
adequate data cleaning is crucial in any data analysis. With
ever-growing dataset sizes and complexities, statisticians and data
analysts find themselves spending a large portion of their time on
data cleaning and on data wrangling. While a computer should never
make unsupervised decisions on what should be done to potential
errors in the dataset, it can still be an extremely useful tool in the
data cleaning process. Some errors can be tracked down and flagged by a
computer without further ado, while other types of errors need an analytic
context in order to shine through. But even in the latter case, well-designed
software can aid the process tremendously by giving the human investigator the
information needed for identifying issues.

Online tools such as OpenRefine (\url{http://openrefine.org/}) and
\proglang{R}-packages such as \pkg{plyr} \citep{plyr}, and
\pkg{data.table} \citep{data.table} have made data wrangling a lot
easier, but only a handful of packages such as \pkg{editrules}
\citep{editrules}, \pkg{validate} \citep{validate}, \pkg{DataCombine}
\citep{DataCombine}, \pkg{janitor} \citep{janitor}, and
\pkg{DescTools} \citep{DescTools} attempt to implement systematic,
reproducible data cleaning.  These packages use different approaches
for data cleaning: \pkg{editrules} and \pkg{validate} provide
frameworks for setting up and checking constraints on the variables,
while \pkg{DataCombine} and \pkg{janitor} both provide a few functions
for identifying problems (e.g, duplicates, dates coded as numbers,
etc.) in data.

While these tools attempt to alleviate the ubiquitous ad hoc approach
to data cleaning, they are primarily intended for the data savvy users
and less so for the general researcher with a knowledge about a specific
field and the context of the available data. The \pkg{dataMaid}
package \citep{dataMaid}
tries to address this by providing a framework that both allows for
extendable, systematic, reproducible data cleaning, and summarizing
findings for researchers from other fields such that they can act as
human experts when tracking down potential errors.

% \begin{itemize}
% \item Makes the point that data cleaning is usually done in a very ad hoc manner
% \item Maybe hints to the discussion later about poor documentation of data cleaning/quality assessment as the status quo for most analysts
% \item Gives a specification of what we mean by data errors/mistakes/whatever. I'm not completely sure this will be clear to everyone and we should probably mention it early on to not lose readers/users.
% \end{itemize}
% }

Data cleaning is a time consuming endeavor, as it inherently requires
human interaction since every dataset is different and the variables
in the dataset can only be understood in the proper context of their
origin. This often requires a collaborative effort between an expert
in the field and a statistician or data scientist, which may be why
the process of proper data cleaning is not always undertaken. In many
situations, these errors are discovered in the process of the data
analysis (e.g., a categorical variable with numeric labels for each
category may be wrongly classified as a quantitative variable or a
variable where all values have erroneously been coded to the same
value), but in other cases a human with knowledge about the data
context area is needed to identify possible mistakes in the data
(e.g., if there are 4 categories for a variable that should only have
3).

@@

As we saw with the \code{check()} function, the summary can be modified
by providing the relevant \code{XXXSummaries} arguments. Setting the
\code{numericSummaries} argument, we can control the summary output by
providing a vector of function names to run for a particular summary. To
only get the median, minimum and the maximum we set
\code{numericSummaries=c("centralValue", "minMax")}:

@@

Adhering to the template above is sufficient for using the freshly
made \code{mySummaryFunction()} in \code{clean()}, but we recommend
furthermore adding the new function to the overview of all summary
functions by converting it to a proper \code{summaryFunction}
object. This is done by calling the \code{summaryFunction()} creator with
the user-defined function as the first argument, and additional arguments
\code{description} (an explanatory text which will be added to the attributes of
the function), and \code{classes} (a vector of variable classes the
user-defined function is intended to be applied to, also stored as an
attribute). In other words, a call on the following form should be made:
\begin{Verbatim}
mySummaryFunction <- summaryFunction(mySummaryFunction,
  description = "[Text describing what the summaryFunction does]",
  classes = c([vector of data types that the function is intended
  for]))
\end{Verbatim}
which adds the new function to the output of an
\code{allSummaryFunctions()} call.
% One comment should be devoted to
% the two attributes of a \code{summaryFunction}.
If the \code{description} argument is left unspecified, the name of the
function (which in this case is \code{"mySummaryFunction"}) will be filled in and
stored under the \code{description} attribute. What happens if the \code{classes} argument is
not specified depends on the type of \code{mySummaryFunction}. If
\code{mySummaryFunction} is constructed as an \code{S3} generic function with associated
methods, the call to \code{summaryFunction()} will automatically produce
a vector of the names of the classes for which the function can be
called. If \code{mySummaryFunction} is not an \code{S3} generic and
\code{classes} is left unspecified, the attribute will simply be
left empty. Note that the helper function \code{allClasses()} might be useful
for filling out the \code{classes} argument, as it simply lists all
available classes in \pkg{dataMaid}:

@@

\subsubsection{Writing a visualFunction}
\code{visualFunction}s are the functions that produce the figures in a
\pkg{dataMaid} output document. Writing a \code{visualFunction} is slightly
more complicated than writing a \code{summaryFunction}. This follows from
the fact that \code{visualFunctions} need to be able to output standalone
code for plots in order for \code{clean()} to build standalone
\pkg{rmarkdown} files. We recommend using the following structure:
\begin{Verbatim}
myVisualFunction <- function(v, vnam, doEval) {
  thisCall <- call("[the name of the function used to produce the plot]",
    v, [additional arguments for the plotting function])
  if (doEval) {
    return(eval(thisCall))
  } else return(deparse(thisCall))
}
\end{Verbatim}

@@

We will now build four new functions and show both how they can be
used interactively and how they can be integrated with the \code{clean()}
function. These four new functions are:
\begin{description}
\item[\code{isID}] A new \code{checkFunction} intended for use in the precheck-stage. This function checks whether a variable consists exclusively of long ($> 10$ characters/digits) entries that are all of equal length, as this might be personal identification codes that we do not wish to print out in the data summary.
\item[\code{mosaicVisual}] A new \code{visualFunction} that produces mosaic plots. This function will be used in the \textit{visualize} step of \code{clean()}.
\item[\code{countZeros}] A new \code{summaryFunction} that counts the number of occurrences of the value \code{0} in a variable. This function will be used in the \textit{summarize} step of \code{clean()}.
\item[\code{identifyColons}] A new \code{checkFunction} that flags variables in which values have colons that appear before and after alphanumerical characters. This is practical for identifying autogenerated interaction effects. This function will be used in the \textit{check} step of \code{clean()}.
\end{description}
These functions are defined in turn below, and afterwards, an example of how they can be called from \code{clean()} is provided.

\subsubsection{isID --- a new checkFunction without problem values}
First, let's define the \code{isID()} function. As this function is not
supposed to list problematic values, it falls within
the category of \code{checkFunctions} represented by
\code{myFullVarCheckFunction()} in the above. We do not particularly wish
to use this function interactively, so we will stick to the minimal
requirements of a \code{checkFunction} used in \code{check()} (see
Table~\ref{table.functionTypes}). The function can then be defined by

@@

\subsubsection{mosiacVisual --- a new visualFunction}
\proglang{R} contains a function, \code{mosiacplot()}, which produces
mosaic plots. We intend to use this existing high-level plotting
function as part of the new visualization function.  We will define
the new function such that it gets the full \pkg{dataMaid}
functionality. This can be done using the following code which sets up
the call using the existing function \code{mosaicplot}.

@@

As \code{mosaicVisual} is now a full-blooded \code{visualFunction}, it
will also be included in the \code{allVisualFunctions()} output table:
\begin{Schunk}
\begin{Sinput}
R> allVisualFunctions()
\end{Sinput}
\begin{Soutput}
------------------------------------------------------------------------------
name             description                     classes                      
---------------- ------------------------------- -----------------------------
mosaicVisual     Mosaic plots using graphics     character, Date, factor,     
                                                 integer, labelled, logical,  
                                                 numeric

@@

Now that we are done with the definition of \code{mosaicVisual()} we can
turn to the next function in line, \code{countZeros}.

@@

As this function computes an integer (the number of zeros),
there is no difference between the entries \code{\$result} and
\code{\$value}. If, on the other hand, the result had been a character
string, extra formatting might be required in the \code{\$result} entry
(such as escaping of quotation marks), and in this scenario, the two
entries would have differed. As the result is returned as a
\code{summaryResult} object, a printing method is automatically called
when \code{countZeros} is used interactively:

@@

YYY en kommentar om noget her, hvad der sker nedenfor

@@

As with the previous two functions, we also change its class. Note,
however, that for \code{checkFunction}s, the function description will
appear in the document produced by \code{clean()} (in the \textit{Data
  cleaning summary} section of the output), so now this is not only
done for the sake of the \code{allCheckFunctions()} output.

\subsubsection{Calling the new summarize/visualize/check functions from clean()}
Now, we are ready to use these new functions in a \code{clean()}
call. The extended \pkg{dataMaid} output document should have the
following modifications, relative to the standard \pkg{dataMaid} output:
\begin{itemize}
\item We want to add the new pre-check function, \code{isID}, to the already existing pre-checks.
\item We wish to change the plot type for all variables to the new mosaic plot.
\item We want the new summary function, \code{countZeros}, to be added to the summaries performed on all variable types but \code{Date} and \code{logical}.
\item We want the new check function, \code{identifyColon}, to be added to the checks performed on \code{character}, \code{factor} and \code{labelled} variables.
\end{itemize}
These options are specified as follows: %\hl{Jeg synes ikke testData
                                %egner sig her. Der er ingen koloner
                                %og CPRvar er et mærkeligt, internt
                                %navn, hvis ikke man kender danske
                                %CPR-numre. Langt de fleste variable
                                %har desuden ingen nuller. Måske skal
                                %der laves et nyt datasæt?}
\begin{Schunk}
\begin{Sinput}
R> data("exampleData")
R> clean(exampleData,
+    preChecks = c("isKey", "isEmpty", "isID"),
+    allVisuals = "mosaicVisual",
+    characterSummaries = c(defaultCharacterSummaries(), "countZeros"),
+    factorSummaries = c(defaultFactorSummaries(), "countZeros"),
+    labelledSummaries = c(defaultLabelledSummaries(), "countZeros"),
+    numericSummaries = c(defaultNumericSummaries(), "countZeros"),
+    integerSummaries = c(defaultIntegerSummaries(), "countZeros"),
+    characterChecks = c(defaultCharacterChecks(), "identifyColons"),
+    factorChecks = c(defaultFactorChecks(), "identifyColons"),
+    labelledCheck = c(defaultLabelledChecks(), "identifyColons"))
\end{Sinput}
\end{Schunk}

>>>>

\section{Introduction}
Though data cleaning might be regarded as a somewhat tedious activity,
adequate data cleaning is crucial in any data analysis. With
ever-growing dataset sizes and complexities, statisticians and data
analysts find themselves spending a large portion of their time on
data cleaning and on data wrangling. While a computer should never
make unsupervised decisions on what should be done to potential
errors in a dataset, it can still be an extremely useful tool in the
data cleaning process. Some errors can be tracked down and flagged by a
computer without further ado, while other types of errors need an analytic
context in order to shine through. But even in the latter case, well-designed
software can aid the process tremendously by giving the human investigator the
information needed for identifying issues.

A number of \proglang{R} packages made for such pre-analysis tools are already 
available, including \pkg{janitor} \citep{janitor}, 
\pkg{plyr} \citep{plyr}, \pkg{data.table} \citep{data.table}, 
\pkg{DataCombine} \citep{DataCombine} , \pkg{validate} \citep{validate}, and
\pkg{DataExplorer} \citep{DataExplorer}. These packages focus on different 
stages of the pre-analysis work, most of which are not really data cleaning.
\pkg{janitor} provides tools for data loading with a
particular emphasis on the challenges of getting neat \code{data.frame}s from 
Microsoft Excel data files. \pkg{plyr}, \pkg{data.table} and \pkg{DataCombine} go a few
steps further by providing a wide array of extremely powerful tools for data wrangling, 
including a number of particularly useful functions for merging and working with
very large datasets. When it comes to actual data cleaning, however, the options are fewer.
\pkg{validate} (and the similar packages \pkg{editrules} and \pkg{deducorrect} from the same 
authors) does offer a few tools for identifying and auto-correcting errors in a dataset, 
but, as the name suggests, the focus is on internal validity rather than 
general data cleaning. In practice, this means that quite elegant tools for e.g. linear 
restraints among the variables in a dataset can be applied, but e.g. looking for potentially
miscoded missing values is not really feasible. The main difference between these two challenges
is the direction in which the data is inspected: While linear constraints work row-wise
with no ambiguity, determining whether or not something is a miscoded missing value 
often requires knowledge about the full variable (e.g. range or data type), and thus
it should be performed column-wise. \pkg{validate} does not allow for user-defined
extensions of the latter type, thereby limiting its data cleaning potential.
Moreover, no tools have been made for documenting the data cleaning process. 
As automatic cleaning options are also supplied in \pkg{validate},  
we find quite a dangerous cocktail where all power is given to the the computer 
with no supervision, neither in real time nor subsequently.

All in all, the large role of data cleaning in any data analysts everyday endeavors is 
hardly matched in the amount of available \proglang{R} software solutions. In particular,
few packages attempt to implement systematic, reproducible data cleaning. And 
while the available tools attempt to alleviate the ubiquitous ad hoc approach
to data cleaning, they are primarily intended for the data savvy users
and less so for the general researcher with a knowledge about a specific
field and the context of the available data. The \pkg{dataMaid}
package \citep{dataMaid} tries to address this by providing a framework that both allows for
extendable, systematic, reproducible data cleaning, and summarizing
findings for researchers from other fields such that they can act as
human experts when tracking down potential errors.

One last package that should be mentioned in this context is \pkg{DataExplorer}. While this
package does not address data cleaning issues per se, its general strategy is quite similar
to that of \pkg{dataMaid} and to the paradigms presented below. This package provides 
a few simple, but practical, tools for exploratory data analysis, including automated 
documentation. Therefore, we find \pkg{DataExplorer} to be a good candidate for a next-step
package after data cleaning is finished.

But no matter how clever software tools we make, data cleaning 
reamins to be a time consuming endeavor, as it inherently requires
human interaction since every dataset is different and the variables
in the dataset can only be understood in the proper context of their
origin. This often requires a collaborative effort between an expert
in the field and a statistician or data scientist, which may be why
the process of proper data cleaning is not always undertaken. In many
situations, these errors are discovered in the process of the data
analysis (e.g., a categorical variable with numeric labels for each
category may be wrongly classified as a quantitative variable or a
variable where all values have erroneously been coded to the same
value), but in other cases a human with knowledge about the data
context area is needed to identify possible mistakes in the data
(e.g., if there are 4 categories for a variable that should only have
3).

@@

As we saw with the \code{check()} function, the summary can be modified
by providing the relevant \code{XXXSummaries} arguments. Setting the
\code{numericSummaries} argument, we can control the summary output by
providing a vector of function names to run for a particular summary. To
only get the median, minimum and the maximum we set
\code{numericSummaries = c("centralValue", "minMax")}:

@@

Adhering to the template above is sufficient for using the freshly
made \code{mySummaryFunction()} in \code{clean()}, but we recommend
furthermore adding the new function to the overview of all summary
functions by converting it to a proper \code{summaryFunction}
object. This is done by calling the \code{summaryFunction()} creator with
the user-defined function as the first argument, and additional arguments
\code{description} (an explanatory text which will be added to the attributes of
the function), and \code{classes} (a vector of variable classes the
user-defined function is intended to be applied to, also stored as an
attribute). In other words, a call on the following form should be made:
\begin{Verbatim}
mySummaryFunction <- summaryFunction(mySummaryFunction,
  description = "[Text describing what the summaryFunction does]",
  classes = c([vector of data types that the function is intended
  for]))
\end{Verbatim}
which adds the new function to the output of an
\code{allSummaryFunctions()} call.
% One comment should be devoted to
% the two attributes of a \code{summaryFunction}.
If the \code{description} argument is left unspecified, the name of the
function (which in this case is \code{"mySummaryFunction"}) will be filled in and
stored under the \code{description} attribute. What happens if the \code{classes} argument is
not specified depends on the type of \code{mySummaryFunction}. If
\code{mySummaryFunction} is constructed as an \code{S3} generic function with associated
methods, the call to \code{summaryFunction()} will automatically produce
a vector of the names of the classes for which the function can be
called. If \code{mySummaryFunction()} is not an \code{S3} generic and
\code{classes} is left unspecified, the attribute will simply be
left empty. Note that the helper function \code{allClasses()} might be useful
for filling out the \code{classes} argument, as it simply lists all
available classes in \pkg{dataMaid}:

@@

\subsubsection{Writing a visualFunction}
\code{visualFunction}s are the functions that produce the figures in a
\pkg{dataMaid} output document. Writing a \code{visualFunction} is slightly
more complicated than writing a \code{summaryFunction}. This follows from
the fact that \code{visualFunction}s need to be able to output standalone
code for plots in order for \code{clean()} to build standalone
\pkg{rmarkdown} files. We recommend using the following structure:
\begin{Verbatim}
myVisualFunction <- function(v, vnam, doEval) {
  thisCall <- call("[the name of the function used to produce the plot]",
    v, [additional arguments for the plotting function])
  if (doEval) {
    return(eval(thisCall))
  } else return(deparse(thisCall))
}
\end{Verbatim}

@@

We will now build four new functions and show both how they can be
used interactively and how they can be integrated with the \code{clean()}
function. These four new functions are:
\begin{description}
\item[\code{isID()}] A new \code{checkFunction} intended for use in the precheck-stage. This function checks whether a variable consists exclusively of long ($> 10$ characters/digits) entries that are all of equal length, as this might be personal identification codes that we do not wish to print out in the data summary.
\item[\code{mosaicVisual()}] A new \code{visualFunction} that produces mosaic plots. This function will be used in the \textit{visualize} step of \code{clean()}.
\item[\code{countZeros()}] A new \code{summaryFunction} that counts the number of occurrences of the value \code{0} in a variable. This function will be used in the \textit{summarize} step of \code{clean()}.
\item[\code{identifyColons()}] A new \code{checkFunction} that flags variables in which values have colons that appear before and after alphanumerical characters. This is practical for identifying autogenerated interaction effects. This function will be used in the \textit{check} step of \code{clean()}.
\end{description}
These functions are defined in turn below, and afterwards, an example of how they can be called from \code{clean()} is provided.

\subsubsection{isID --- a new checkFunction without problem values}
First, let's define the \code{isID()} function. As this function is not
supposed to list problematic values, it falls within
the category of \code{checkFunction}s represented by
\code{myFullVarCheckFunction()} in the above. We do not particularly wish
to use this function interactively, so we will stick to the minimal
requirements of a \code{checkFunction} used in \code{check()} (see
Table~\ref{table.functionTypes}). The function can then be defined by

@@

\subsubsection{mosiacVisual --- a new visualFunction}
\proglang{R} contains a function, \code{mosiacplot()}, which produces
mosaic plots. We intend to use this existing high-level plotting
function as part of the new visualization function.  We will define
the new function such that it gets the full \pkg{dataMaid}
functionality. This can be done using the following code which sets up
the call using the existing function \code{mosaicplot()}.

@@

As \code{mosaicVisual()} is now a full-blooded \code{visualFunction}, it
will also be included in the \code{allVisualFunctions()} output table:
\begin{Schunk}
\begin{Sinput}
R> allVisualFunctions()
\end{Sinput}
\begin{Soutput}
------------------------------------------------------------------------------
name             description                     classes                      
---------------- ------------------------------- -----------------------------
mosaicVisual     Mosaic plots using graphics     character, Date, factor,     
                                                 integer, labelled, logical,  
                                                 numeric

@@

Now that we are done with the definition of \code{mosaicVisual()} we can
turn to the next function in line, \code{countZeros()}.

@@

As this function computes an integer (the number of zeros),
there is no difference between the entries \code{\$result} and
\code{\$value}. If, on the other hand, the result had been a character
string, extra formatting might be required in the \code{\$result} entry
(such as escaping of quotation marks), and in this scenario, the two
entries would have differed. As the result is returned as a
\code{summaryResult} object, a printing method is automatically called
when \code{countZeros()} is used interactively:

@@

Once again, we change the class of the function so that it becomes a proper \code{checkFunction} object:

@@

Note, that for \code{checkFunction}s, the function description will
appear in the document produced by \code{clean()} (in the \textit{Data
  cleaning summary} section of the output), so for this type of function, 
the change of class is not only done for the sake of the \code{allCheckFunctions()} output.

\subsubsection{Calling the new summarize/visualize/check functions from clean()}
Now, we are ready to use these new functions in a \code{clean()}
call. The extended \pkg{dataMaid} output document should have the
following modifications, relative to the standard \pkg{dataMaid} output:
\begin{itemize}
\item We want to add the new pre-check function, \code{isID()}, to the already existing pre-checks.
\item We wish to change the plot type for all variables to the new mosaic plot.
\item We want the new summary function, \code{countZeros()}, to be added to the summaries performed on all variable types but \code{Date} and \code{logical}.
\item We want the new check function, \code{identifyColons()}, to be added to the checks performed on \code{character}, \code{factor} and \code{labelled} variables.
\end{itemize}
These options are specified as follows: 
\begin{Schunk}
\begin{Sinput}
R> data("exampleData")
R> clean(exampleData,
+    preChecks = c("isKey", "isEmpty", "isID"),
+    allVisuals = "mosaicVisual",
+    characterSummaries = c(defaultCharacterSummaries(), "countZeros"),
+    factorSummaries = c(defaultFactorSummaries(), "countZeros"),
+    labelledSummaries = c(defaultLabelledSummaries(), "countZeros"),
+    numericSummaries = c(defaultNumericSummaries(), "countZeros"),
+    integerSummaries = c(defaultIntegerSummaries(), "countZeros"),
+    characterChecks = c(defaultCharacterChecks(), "identifyColons"),
+    factorChecks = c(defaultFactorChecks(), "identifyColons"),
+    labelledCheck = c(defaultLabelledChecks(), "identifyColons"))
\end{Sinput}
\end{Schunk}

### 2017-01-29 latex/dataMaid_toyData.Rmd
Updated article

---
dataMaid: yes
title: toyData
subtitle: "Autogenerated data summary from dataMaid"
date: "`r Sys.Date()`"
output: pdf_document
documentclass: report
header-includes:
  - \renewcommand{\chaptername}{Part}
  - \newcommand{\fullline}{\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}}
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library(ggplot2)
library(pander)
```
# Data cleaning summary
The dataset examined has the following dimensions:

@@

* Only variables that were deemed potentially problematic are included in this summary.

@@

# Variable list
## **var5**

>>>>

---
dataMaid: yes
title: toyData
subtitle: "Autogenerated data summary from dataMaid"
date: "`r Sys.Date()`"
output: pdf_document
documentclass: report
header-includes:
  - \renewcommand{\chaptername}{Part}
  - \newcommand{\fullline}{\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}}
  - \newcommand{\bminione}{\begin{minipage}{0.75 \textwidth}}
  - \newcommand{\bminitwo}{\begin{minipage}{0.25 \textwidth}}
  - \newcommand{\emini}{\end{minipage}}
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library(ggplot2)
library(pander)
```
# Data cleaning summary
The dataset examined has the following dimensions:

@@

@@

# Variable list
## **var1**

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                    factor

Number of missing obs.      2 (13.33 %)

Number of unique values               2

Mode                              "red"
---------------------------------------

\emini
\bminitwo
```{r Var-1-var1, echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
qplot(x = structure(c(2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 
1L, 1L, 1L), .Label = c("blue", "red"), class = "factor", na.action = structure(14:15, class = "omit")), 
    geom = "bar", xlab = "", main = "var1")
```
\emini

- Note that the following levels have at most five observations: \"blue\".

## **var2**

\bminione

------------------------------------
Feature                       Result
------------------------- ----------
Variable type                numeric

Number of missing obs.      3 (20 %)

Number of unique values            8

Median                           4.5

1st and 3rd quartiles        1.75; 6

Min. and max.                 1; 999
------------------------------------

\emini
\bminitwo
```{r Var-2-var2, echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
qplot(x = c(1, 1, 1, 2, 2, 6, 6, 6, 999, 4, 82, 5), geom = "histogram", 
    xlab = "", main = "var2", bins = 20)
```
\emini

- The following suspected missing value codes enter as regular values: \"999\", \"NaN\".

- Note that the following possible outlier values were detected: \"82\", \"999\".

## **var3**

\bminione

-----------------------------------
Feature                      Result
------------------------- ---------
Variable type                factor

Number of missing obs.      0 (0 %)

Number of unique values           7

Mode                            "a"
-----------------------------------

\emini
\bminitwo
```{r Var-3-var3, echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
qplot(x = structure(c(3L, 3L, 3L, 3L, 3L, 4L, 4L, 4L, 5L, 5L, 
5L, 2L, 1L, 6L, 7L), .Label = c(" ", ".", "a", "b", "c", "other", 
"OTHER"), class = "factor"), geom = "bar", xlab = "", main = "var3")
```
\emini

- The following suspected missing value codes enter as regular values: \" \", \".\".

- The following values appear with prefixed or suffixed white space: \" \".

- Note that the following levels have at most five observations: \" \", \".\", \"a\", \"b\", \"c\", \"other\", \"OTHER\".

- Note that there might be case problems with the following levels: \"other\", \"OTHER\".

## **var4**

\bminione

---------------------------------------
Feature                          Result
------------------------- -------------
Variable type                   numeric

Number of missing obs.          0 (0 %)

Number of unique values              15

Median                             0.33

1st and 3rd quartiles       -0.62; 0.66

Min. and max.                -2.21; 1.6
---------------------------------------

\emini
\bminitwo
```{r Var-4-var4, echo=FALSE, fig.width=4, fig.height=3, message=FALSE, warning=FALSE}
qplot(x = c(-0.626453810742332, 0.183643324222082, -0.835628612410047, 
1.59528080213779, 0.329507771815361, -0.820468384118015, 0.487429052428485, 
0.738324705129217, 0.575781351653492, -0.305388387156356, 1.51178116845085, 
0.389843236411431, -0.621240580541804, -2.2146998871775, 1.12493091814311
), geom = "histogram", xlab = "", main = "var4", bins = 20)
```
\emini

- Note that the following possible outlier values were detected: \"1.12\", \"1.51\", \"1.6\".

## **var5**
